Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-10 main.tex
implemented todos until (not including) section 6.C

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{balance}

@@

Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
\new{Workflow tasks themselves have no memory requirements for their computations,
but they have input and output files that need to be stored in the memory.}
A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a workflow DAG is provided,
as well as an integer linear programming (ILP) solution to the scheduling problem.
The memory model \new{requires deleting all input files when the task starts and adding all output files to memory.}
\AB{Is it not when task completes? We need input files while processing the task, correct?}

@@

De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) adaptive scheduling algorithm
for clouds.
They solve a set of linear equations\todo{Mis\-lea\-ding, TBD!} that represent the cost of an execution based on the criteria.
The authors test four scenarios -- one preferring each criterion and a balanced one.
The algorithm chooses the best virtual machine for each next task based on the cost given by the model.
The authors use workflows with less than ten tasks, but repeat them so that the execution has up to 200 tasks.
%They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.
%   The authors use provenance data to make scheduling decisions.

@@

Not all tasks have historical runtime data stored in the tables.
In fact, for two workflows, Bader~\etal do not provide data for more than 50\% of the tasks.
For two more, around 40\% of the tasks have no historical runtime data stored.
Hence, in the absence of historical data about a task, we give it fixed weights:
an execution time of $1$, a memory requirement of $50 MB$, and files written and received of $1KB$.
These values align with the findings of Ref.~\cite{lotaru} about small tasks.
%
 %   \skug{insert more abt how the runtime system hanfles data reads}

@@

Similarly to the default cluster, we observe that the makespan of \heftmm is usually higher
than with \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but the \heft schedules are
almost all invalid. It is thus worthwhile to resort to \heftmm for large workflows
in a constrained cluster, since tasks are processed in an order that minimizes
the memory usage of schedule.
\new{Due to a varying nature of the workflow generator, some larger workflows can have smaller makespans than their
smaller counterparts due to more parallelism at nodes with higher out-degree or other factors of the workflow's
internal composition.\todo{TBD: Why here?}}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm  %\new{ 
    when there is no recomputation. Smaller is better.}
    \label{fig:updates-ms}
%    \vspace{-0.3cm}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{balance}

@@

Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
\new{Workflow tasks themselves have no memory requirements for their computations,
but they have input and output files that need to be stored in the memory.}
A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a workflow DAG is provided,
as well as an integer linear programming (ILP) solution to the scheduling problem.
The memory model \new{ includes no memory requirement of the task itself, only the weights of incoming and outgoing edges.
When the task starts, all input files are deleted  and all output files are added to memory.}

@@

De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) \new{cost model and an adaptive
 scheduling algorithm for clouds (scheduling virtual machines).
The greedy algorithm based on this cost model  works in 4 steps, choosing the best resources type to execute the virtual
machine on, producing new cloud activities, setting up the granularity factor, and finally adapting the amount of resources
to fit the budget.}
The authors test four scenarios -- one preferring each criterion in the cost model and a balanced one.
The authors use workflows with less than ten tasks, but repeat them so that the execution has up to 200 tasks.
%They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.
%   The authors use provenance data to make scheduling decisions.

@@

Not all tasks have historical runtime data stored in the tables.
In fact, for two workflows, Bader~\etal do not provide data for more than 50\% of the tasks.
For two more, around 40\% of the tasks have no historical runtime data stored.
Hence, in the absence of historical data about a task, we give it fixed weights:
an execution time of $1$, a memory requirement of $50 MB$, and files written and received of $1KB$.
These values align with the findings of Ref.~\cite{lotaru} about small tasks.

\new{Due to a varying nature of the workflow generator, some workflows can have smaller makespans than their
smaller counterparts due to more parallelism at nodes with higher out-degree or other factors of the workflow's
internal composition.}

@@

Similarly to the default cluster, we observe that the makespan of \heftmm is usually higher
than with \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but the \heft schedules are
almost all invalid. It is thus worthwhile to resort to \heftmm for large workflows
in a constrained cluster, since tasks are processed in an order that minimizes
the memory usage of schedule.
\new{Note how the relative makespan does not grow steadily with the size of the workflows.
Rather, it grows at the beginning, but then falls for the sizes of workflows where scheduling becomes problematic.
This indicates that \heft schedules become relatively worse for larger workflows, in addition to being unfeasible memory-wise.
Finally, the relative makespan for the largest workflows, the ones for which only \heftmm can produce valid schedules,
is growing larger again.
This is due to the highest degree of memory adaptation necessary to produce a valid schedule.
}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{
    \new{Relative makespan improvement of \heftbl, \heftblc, \heftmm and baseline \heft against
    the execution with the same heuristic, but without recomputation. Higher is better. } }
    \label{fig:updates-ms}
%    \vspace{-0.3cm}
\end{figure}
